---
title: "615 movie"
author: "HongnaSu"
date: "2024-11-06"
output:
  pdf_document:
   latex_engine: xelatex
---


```{r}
library("tidyverse")
library("topicmodels")
library("tidytext")
library("lexicon")
library("factoextra")
library("wordcloud")   
library("ldatuning")       
library("ggplot2") 
library("rmarkdown")
```


```{r}
movie<-read.csv("movie_plots_with_genres.csv")
movie
```



```{r pressure, echo=FALSE}
movies <- read.csv("movie_plots.csv")
plots_by_words <- movies %>% unnest_tokens(word, Plot) %>%
  anti_join(stop_words) %>%
  count(Movie.Name, word, sort = TRUE)

data("freq_first_names")
first_names <- tolower(freq_first_names$Name)
plot_word_counts <- plots_by_words %>%
  filter(!(word %in% first_names))

```
```{r}
library(ldatuning)
library(tidyverse)
dtm <- plot_word_counts %>%
  cast_dtm(Movie.Name, word, n)
topic_range <- seq(2, 50, by = 5)
metrics <- c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014")
control_params <- list(seed = 1234)
result <- FindTopicsNumber(
  dtm = dtm,
  topics = topic_range,
  metrics = metrics,
  method = "Gibbs",
  control = control_params,
  mc.cores = 2,
  verbose = TRUE
)
FindTopicsNumber_plot(result)

```

```{r}
library(tidyverse)
library(topicmodels)
optimal_k <- 30
lda_model <- LDA(dtm, k = optimal_k, control = list(seed = 1234))

gamma_matrix <- posterior(lda_model)$topics
beta_matrix <- posterior(lda_model)$terms
if (is.null(gamma_matrix) || is.null(beta_matrix)) {
  stop("LDA model did not return valid topic or term matrices.")
}

plots_gamma <- as.data.frame(gamma_matrix) %>%
  mutate(document = rownames(gamma_matrix))

plots_beta <- as.data.frame(beta_matrix) %>%
  mutate(term = rownames(beta_matrix))

plots_gamma_tidy <- plots_gamma %>%
  pivot_longer(cols = -document, names_to = "topic", values_to = "gamma")

plots_beta_tidy <- plots_beta %>%
  pivot_longer(cols = -term, names_to = "topic", values_to = "beta")
head(plots_gamma_tidy)
head(plots_beta_tidy)

```

```{r}
plots_gamma_tidy%>%
  ggplot(aes(topic, gamma, fill = factor(document))) +
  geom_boxplot(show.legend = FALSE) +
  labs(title = "Document-Topic Gamma Distribution", x = "Topic", y = "Gamma (Probability)")


```

```{r}
library(tidytext)

top_terms <- plots_beta_tidy %>%
  group_by(topic) %>% 
  slice_max(beta, n = 10) %>%  
  ungroup() %>% 
  arrange(topic, -beta)
top_terms %>%
  ggplot(aes(beta, reorder_within(term, beta, topic), fill = factor(topic))) 
```

```{r}
plots_gamma_wider <- plots_gamma_tidy %>% pivot_wider(
  names_from = topic,
  values_from = gamma
) %>%
  drop_na()

set.seed(123)
cluster <- kmeans(plots_gamma_wider %>% select(-document), centers = 8)
fviz_cluster(cluster, data = plots_gamma_wider %>% select(-document), geom = "point") +
  labs(title = "K-means Clustering of Movies by Topic Gammas")

```


#Interpret
Scree Plot: Helps identify the optimal number of topics by displaying coherence scores for different topic counts.
Gamma Plot: Illustrates how strongly each movie is associated with each topic.
Beta Plot: Highlights the most representative words for each topic based on their beta values.
Cluster Plot: Visualizes groups of movies with similar themes based on their topic distributions.
Word Cloud: Offers a visual representation of the most significant words across topics, with word size indicating importance.

